RIScatter: Unifying\\Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-08-30 main.tex
:pencil: Add paradigm plots

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

@@

	% Simulation results demonstrate RIScatter can exploit the additional propagation paths to provide a smooth transition between backscatter modulation and passive beamforming, which

@@

	% The three multiple access schemes are compared, and extensive numerical results show that RSMA provides a smooth transition between SDMA and NOMA and outperforms them both in a wide range of network loads (underloaded and overloaded regimes) and user deployments (with a diversity of channel directions, channel strengths, and qualities of channel state information at the transmitter). Moreover, RSMA provides rate and QoS enhancements over NOMA at a lower computational complexity for the transmit scheduler and the receivers (number of SIC layers).

@@

	The node harvests energy from emitted wave and embeds information over scattered signal in a sustainable and controllable manner.

@@

	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connection in between.
	It eliminates the need of dedicated power source, carrier emitter, and frequency spectrum, bringing more opportunities to low-power communications.

@@

@@

	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:uniscatter}.
	\end{subsection}
\end{section}

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:uniscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:uniscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

		As shown in Fig. \subref*{fi:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fi:uniscatter_node}
		\end{figure*}
	\end{subsection}

@@

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{uniscatter_network.eps_tex}
			}
			\caption{A single-user multi-node RIScatter system.}
			\label{fi:uniscatter_network}
		\end{figure}
		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:uniscatter_network}.
		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed RIScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.

@@

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
	\end{subsection}
	\label{se:uniscatter}
\end{section}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:uniscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Ricean fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.

>>>>

% PGF/TikZ
\usetikzlibrary{arrows,calc,matrix,patterns,plotmarks,positioning,shapes}
\usepgfplotslibrary{groupplots,patchplots}
\pgfplotsset{compat=newest}

@@

@@

@@

	The node harvests energy from impinging wave and embeds information over scattered signal in a sustainable and controllable manner.

@@

	In \gls{ambc} \cite{Liu2013b}, interactive nodes recycle ambient signals generated by legacy transmitters (e.g., radio, television, and Wi-Fi) to harvest energy and establish connections.
	It eliminates the need of dedicated power source, carrier emitter and frequency spectrum, bringing more opportunities to low-power communications.

@@

	\begin{figure}[!t]
		\centering
		\subfloat[Monostatic \gls{bc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/monostatic_backscatter_communication.tex}
			}
			\label{fi:monostatic_backscatter_communication}
		}
		\subfloat[Bistatic \gls{bc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/bistatic_backscatter_communication.tex}
			}
			\label{fi:bistatic_backscatter_communication}
		}
		\\
		\subfloat[\gls{ambc}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/ambient_backscatter_communication.tex}
			}
			\label{fi:ambient_backscatter_communication}
		}
		\subfloat[\gls{sr}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/symbiotic_radio.tex}
			}
			\label{fi:symbiotic_radio}
		}
		\\
		\subfloat[\gls{ris}]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/reconfigurable_intelligent_surface.tex}
			}
			\label{fi:reconfigurable_intelligent_surface}
		}
		\subfloat[RIScatter]{
			\resizebox{0.48\linewidth}{!}{
				\input{assets/illustration/riscatter.tex}
			}
			\label{fi:riscatter}
		}
		\caption{
			Paradigms for scattering applications.
		}
		\label{fi:scatter_comparison}
	\end{figure}

@@

	\begin{subsection}{Opportunities}
		We have seen conventional scattering applications as \gls{bc}, \gls{sr} and \gls{ris} using the reflection pattern \eqref{eq:reflection_pattern_antenna}, \eqref{eq:reflection_pattern_metamaterial} for either backscatter modulation \eqref{eq:backscatter_modulation} or passive beamforming \eqref{eq:passive_beamforming}.
		A natural but critical question is, for a given scatterer with pre-determined reflection pattern set, \emph{can we softly bridge backscatter modulation and passive beamforming by appropriate reflection design?}
		This question is answered in Section \ref{se:riscatter}.
	\end{subsection}
\end{section}

\begin{section}{RIScatter}
	Using shared spectrum, energy and infrastructures, RIScatter is a novel passive communication/assistance protocol that generalizes \gls{bc}, \gls{sr} and \gls{ris} in a \emph{geographically} and \emph{probabilistically} distributed manner.
	In particular, passive RIScatter nodes located at different places ride over an active legacy transmission in a flexible and mutualistic manner, while practical RIScatter receiver cooperatively decodes both primary and backscatter links under the benefits of backscatter modulation and passive beamforming.
	% TODO compare BC, SR and IRS
	\begin{subsection}{RIScatter Nodes}
		Based on link priority and \gls{csi}, RIScatter nodes adapt the \emph{state input probability distribution} of antenna-based scatterers to unify backscatter modulation and passive beamforming.
		The scattering sources of \gls{bc}/\gls{sr} and reflecting elements of \gls{ris} can be viewed as its extreme cases, where the input distribution boils down to equiprobable and degenerate, respectively.
		\begin{figure}[!t]
			\centering
			\subfloat[Input Distribution]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/input_distribution.tex}
				}
				\label{fi:input_distribution}
			}
			\\
			\subfloat[Time Block]{
				\resizebox{0.8\columnwidth}{!}{
					\input{assets/illustration/time_block.tex}
				}
				\label{fi:time_block}
			}
			\caption{
				Input probability distribution and time block structure of \gls{bc}, \gls{sr}, \gls{ris}, and RIScatter.
				$T_s$ and $T_c$ respectively denote the primary and backscatter symbol period.
				Within channel coherence time, RIScatter nodes semi-randomly select reflection state for each backscatter symbol block under the guidance of input probability distribution.
			}
			\label{fi:riscatter_distribution}
		\end{figure}
		As illustrated in Fig. \ref{fi:riscatter_distribution}, instead of always using fully random or deterministic reflection pattern over time, each RIScatter node can \emph{flexibly adjust} its input distribution to balance information encoding and channel reconfiguration.
		That is, it semi-randomly select the reflection state per backscatter symbol block under the guidance of input probability $P(\Gamma_m)$ for state $m$.
		Such an adaptive backscatter channel coding coincides with \gls{ris} when primary link is absolutely prioritized, and outperforms the uncoded equiprobable inputs of \gls{bc}/\gls{sr} when backscatter link is absolutely prioritized.
		Besides, the dispersed characteristics of RIScatter nodes and legacy users avoids the development optimization and allows uniformly good performance for both links.

		As shown in Fig. \subref*{fi:block_diagram}, RIScatter nodes can be implemented over readily available passive backscatter devices with energy harvester and information decoder.
		Its equivalent circuit and scatter model are presented in Fig. \subref*{fi:equivalent_circuit} and \subref*{fi:scatter_model}.
		When activated by primary transmitter, each node harvests a proportion of the impinging wave for its own operation, decode the embedded coordination information for input distribution control, then applies a potentially random phase shift on the reradiated signal due to backscatter modulation.
		Energy harvesting and information decoding at passive RIScatter nodes can be realized using conventional power-splitting or time-sharing \gls{swipt} protocols \cite{Clerckx2019} or integrated energy-information receiver with pulse position modulated signal \cite{Kim2021a}.
		Besides, relevant \gls{csi} can be acquired using either traditional sequential methods \cite{Bharadia2015,Yang2015b,Guo2019g} or the state-of-the-art parallel approach \cite{Jin2021a}.
		In the following context, we assume perfect primary-total-backscatter coordination and perfect channel estimation for all links.
		\begin{figure*}[!t]
			\centering
			\subfloat[Block Diagram]{
				\resizebox{0.32\linewidth}{!}{
					\input{assets/illustration/block_diagram.tex}
				}
				\label{fi:block_diagram}
			}
			\subfloat[Equivalent Circuit]{
				\resizebox{0.37\linewidth}{!}{
					\input{assets/illustration/equivalent_circuit.tex}
				}
				\label{fi:equivalent_circuit}
			}
			\subfloat[Scatter Model]{
				\resizebox{0.28\linewidth}{!}{
					\input{assets/illustration/scatter_model.tex}
				}
				\label{fi:scatter_model}
			}
			\caption{
			Block diagram, equivalent circuit, and scatter model of a RIScatter node.
			The solid and dashed vectors represent signal and energy flows.
			The scattering antenna behaves as a constant power source, where the voltage $V_0$ and current $I_0$ are introduced by incident electric field $\vec{E}_{\mathrm{I}}$ and magnetic field $\vec{H}_{\mathrm{I}}$ \cite{Huang2021}.
			}
			\label{fi:riscatter_node}
		\end{figure*}
	\end{subsection}

@@

	\begin{subsection}{System Model}
		\begin{figure}[!t]
			\centering
			\def\svgwidth{0.8\columnwidth}
			\footnotesize{
				\import{assets/illustration/}{riscatter_network.pdf_tex}
			}
			\caption{A single-user multi-node RIScatter system.}
			\label{fi:riscatter_network}
		\end{figure}
		To demonstrate the advantages of RIScatter, we consider a single-user multi-node \gls{miso} RIScatter system as shown in Fig. \ref{fi:riscatter_network}.
		In the primary active point-to-point system, a $Q$-antenna \gls{ap} transmits to a single-antenna user assisted by $K$ nearby single-antenna RIScatter nodes with $M$ reflection states.
		In the secondary backscatter \gls{mac} system, the \gls{ap} serves as the carrier emitter, the distributed RIScatter nodes modulate information over reradiated \gls{rf} signals, and the user decodes their messages.
		For simplicity, we consider a quasi-static block fading model where channels remain constant within coherence block and vary independently between consecutive blocks.
		Due to the physical constraints of load switching speed, we assume the backscatter over primary symbol period ratio is an integer $N \gg 1$.
		We also omit the signal reflected by two or more times and ignore the propagation time difference of different paths.

@@

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
	\end{subsection}
	\label{se:riscatter}
\end{section}

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision design for the RIScatter system in Fig. \ref{fi:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter}, $K=2$ RIScatter nodes are randomly dropped within a disk of radius \qty{2}{\meter} centered at the user, the \gls{ap} is with $Q=4$ transmit antennas and an average power budget $P=\qty{36}{\dBm}$, the nodes employs \num{4}-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$, and the symbol period ratio is $N=20$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma
	\end{equation}
	together with a Ricean fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at distance $d_0=\qty{1}{\meter}$, $\kappa$ is the Ricean $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with entries of unit magnitude, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with entries in standard \gls{iid} \gls{cscg} distribution.
	We choose $\gamma_{\mathrm{D}}=2.6$, $\gamma_{\mathrm{F}}=2.4$, $\gamma_{\mathrm{B}}=2$, and $\kappa_{\mathrm{D}}=\kappa_{\mathrm{F}}=\kappa_{\mathrm{B}}=5$ for direct, forward and backward links.
	The finite threshold domain $\mathcal{T}$ comes from $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence level $1-\varepsilon$, where $b=7$ and $\varepsilon=\num{1e-3}$.
	All achievable rate curves/regions are averaged over \num{3000} realizations, and the parameters remain fixed unless otherwise specified.
